Reionization Planck 2018 Notes

### 2020-06-24 results/notes.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{PC chains for zmax = 30. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax50/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax50_pliklite_post_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{PC chains for zmax = 50. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax50_pliklite_post.pdf}
\caption{Comparing zmax = 30 and 50 PC chains using Planck 2018 original lowE likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE). Note that the zmax = 30 uses 5 PCs, whereas the zmax = 50 chains uses 7 PCs.
}
\label{fig:tau_gtz_zmax_30_vs_50_simall_EE}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{Same as Fig.~\ref{fig:tau_gtz_zmax_30_vs_50_simall_EE}, but for the srollv2 likelihood (plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

%Optional
\begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{PC zmax = 30 vs tanh chains with plik\_full\_TTTEEE for the high-l likelihood.
}
\label{fig:}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{results/cosmomc_runs/two_parameter_model/tauhi_taulo_chains/pl18_tanh_highz_test2_run1_2D.pdf}
\caption{Direct MCMC chains of the two-parameter model with \tauhi and \taulo: 2D plot of \tauhi and \taulo.
}
\label{fig:two_parameter_model_2D_plot}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{   results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_xe_full.pdf}
\caption{PC zmax = 30 vs tanh chains with plik lite and srollv2, with ML model from two-parameter model for \tauhi restricted to $>$ 0.02 (ML model: \tauhi = 0.0206, \taulo = 0.0414).
}
\label{fig:two_parameter_model_ML}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{  results/cosmomc_runs/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_PC_proj.pdf}
\caption{Same as Fig.~\ref{fig:two_parameter_model_ML} except the blue curve is a PC projection instead of the full xe(z) of the model.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{   results/cosmomc_runs/two_parameter_model/plot_1D_tau_hi_pl18_tanh_highz_fixed_taulo_test2_run1.pdf}
\caption{Chains for two-parameter model with fixed \taulo = 0.04: 1D distribution of \tauhi (not sure what this is for anymore...).}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{python_kde_test/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{KDE tests in python for the tanh model with various f = 0.1, 0.12, 0.14. It is probably safest to use any of these, so given the smaller f the better, f = 0.1 is probably the best choice here.
}
\label{fig:}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax30_pliklite_srollv2_0930.pdf}
\caption{PC chains for zmax = 30. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/pl18_plots_zmax50/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax50_pliklite_post_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{PC chains for zmax = 50. Planck 2018 original lowE vs srollv2 likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE vs plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_post_0930_and_pl18_pc_zmax50_pliklite_post.pdf}
\caption{Comparing zmax = 30 and 50 PC chains using Planck 2018 original lowE likelihood (plik\_lite\_TTTEEE + lowl + simall\_EE). Note that the zmax = 30 uses 5 PCs, whereas the zmax = 50 chains uses 7 PCs.
}
\label{fig:tau_gtz_zmax_30_vs_50_simall_EE}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{Same as Fig.~\ref{fig:tau_gtz_zmax_30_vs_50_simall_EE}, but for the srollv2 likelihood (plik\_lite\_TTTEEE + lowl + sroll2\_EE).
}
\label{fig:}
\end{figure}

%Optional
\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_plikfull_and_pl18_tanh_post_plikfull.pdf}
\caption{PC zmax = 30 vs tanh chains with plik\_full\_TTTEEE for the high-l likelihood.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{results/direct_mcmc/two_parameter_model/tauhi_taulo_chains/pl18_tanh_highz_test2_run1_tri.png}
\caption{Direct MCMC chains of the two-parameter model with \tauhi and \taulo: triangle plot of \tauhi and \taulo.
}
\label{fig:two_parameter_model_2D_plot}
\end{figure}

 \begin{figure}
\includegraphics[width=0.65\textwidth]{   results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_xe_full.pdf}
\caption{PC zmax = 30 vs tanh chains with plik lite and srollv2, with ML model from two-parameter model for \tauhi restricted to $>$ 0.02 (ML model: \tauhi = 0.0206, \taulo = 0.0414).
}
\label{fig:two_parameter_model_ML}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{  results/direct_mcmc/pl18_plots_zmax30/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax30_pliklite_srollv2_0930_and_pl18_tanh_post_pliklite_srollv2_with_added_two_parameter_ML_PC_proj.pdf}
\caption{Same as Fig.~\ref{fig:two_parameter_model_ML} except the blue curve is a PC projection instead of the full xe(z) of the model.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{   results/direct_mcmc/two_parameter_model/fixed_taulo_chains/plot_1D_tau_hi_pl18_tanh_highz_fixed_taulo_test2_run1.pdf}
\caption{Chains for two-parameter model with fixed \taulo = 0.04: 1D distribution of \tauhi (not sure what this is for anymore...).}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{python_kde/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_fraccov_1p0_burnin_10000_yes_norm_gaussian0p1_0p12_0p14.pdf}
\caption{KDE tests in python for the tanh model with various f = 0.1, 0.12, 0.14. It is probably safest to use any of these, so given the smaller f the better, f = 0.1 is probably the best choice here.
}
\label{fig:}
\end{figure}
